\chapter{Assembly}

\addthumb{\LARGE\quad Assembly}{\huge \textbf{  \ding{81}}}{white}{titlepagecolor!40}

\section{Guide}
\begin{enumerate}[label=\bfseries Step \arabic*]
\item \hfill \\
Part [15] is mounted underneath part [7] using two 4.5mm bolts and nuts.
\item \hfill \\
A motor (part [1]) is attached on the back of part [7] using four M3 bolts. Choose the holes on part [7] so that when a camera is mounted in one of the two bottom holes, the camera’s center of mass will align with the motor’s rotational axis.
\item \hfill \\
Mount part [8] on the motor (part [1]) using three M2.5 bolts.
\item The case of the BaseCam main board is placed at position [14] at the back of part [8] using a reattachable fastener of your choice.
\item \hfill \\
The BaseCam main board is mounted into the case.
\item \hfill \\
Put a new motor on part [8] using four M3 bolts.
\item \hfill \\
Part [9] is put through part [2] and attached to part [8] using a 4.5mm screw in one side, and
three M2.5 bolts on the motor (part [1])
\item \hfill \\
Put part [4] and part [5] together using M3 bolts and nuts, to assemble the handlebar.
\item \hfill \\
Mount the last motor (part [1]) on the handlebar using three 2.5mm bolts. If the onehanded grip (part [10]) is used, it needs to be mounted in between the handlebar and the new motor.
\item \hfill \\
Put the handlebar through part [2] and mounted to the upper motor using four M3 bolts.
\item \hfill \\
Use two M4 bolts and nuts to fasten and position the camera’s center of mass so it aligns.
with the motor’s rotational axis.
\item \hfill \\
Mount both parts [6] to the handlebar using two long (approx. 80mm length) woodscrews.
\item \hfill \\
Put the joystick into part [3] and mount it to the right part [6] using a tie-wrap. Wire the joystick by connecting the onboard 5V and GND to the joystick and connect the BTN on the mainboard to the SW and GND on the joystick. This means that you have to merge two cables into one GND pin on the joystick. Lastly, the VRy and VRx on the joystick go into RX\_ROLL and RX\_PITCH on the mainboard.
\item \hfill \\
If part [10] is mounted, attach part [11] using proper sized woodscrews.
\item \hfill \\
The case for the BaseCam yaw board is placed at position [13] at the back of part [8] using a reattachable fastener of your choice.
\item \hfill \\
The BaseCam yaw board is mounted into the case.
\item \hfill \\
The battery is placed at position [12] at the back of part [8] using a reattachable fastener of your choice.
\end{enumerate}